Contextual Identity: Towards Usable Privacy

### 2013-03-04 paper.tex
rewrites may be ending soon?

\paragraph{Multiple accounts}
The long-time existence of support for multiple accounts in email clients
suggests that many users have multiple email identifiers, which could be
considered as a proxy for identity if tied to service accounts. Similarly, data
suggests that a large minority of Twitter users have multiple Twitter accounts,
and the plethora of cross-posting or syndication software from one social
network to another suggests that many users take advantage of multiple social
networks~\cite{twitter}.

@@

\paragraph{Linking between profiles}

-link from fb profile to blog
-link between services

@@

- Chrome sync
- picl
- xmarks

@@

@@

Service providers are highly incentivized to make linking identities easy, so
we concentrate on tools to help separate and curate identities.

@@

\paragraph{Mitigating explicit linkage} Federated login services can prevent
linking contextual identities to the same user identifier.  For example, a
federated login service that supported multiple identifiers could prevent the
user from associating the same identifier to radically different
contextual identities, such as ones for dating and professional use.

@@

\paragraph{Expiring posts}
Humans don't have perfect memories, so perhaps social networks shouldn't either
~\cite{delete}. Many users already engage in manual auditing and deletion
of old posts~\cite{fbtips2}. A better solution would be to build tools that let
the user manage this more easily through an API: both Twitter and Facebook
provide APIs for post deletion\footnote{Google Plus offers a read-only API.}.

@@

\section{Summary}
People have multiple contextual identities. Sharing personal information in
appropriate contexts fosters positive human interaction.  We hope that
contextual identity will serve as a useful notion for developers to understand
their users' privacy needs, and to develop tools that allow users to act in
their contextual identities in a spontaneous, relaxed, and interesting way.

>>>>

\paragraph{Multiple accounts}
The long-time existence of support for multiple accounts in email clients
suggests that many users have multiple email identifiers, which could be
considered as a proxy for identity if tied to service accounts. Similarly, data
suggests that a large minority of Twitter users have multiple Twitter
accounts~\cite{twitter}.

@@

\paragraph{Building social graphs}

Users can explicitly create links between contextual identities, e.g.  linking
to their blog from their Flickr profile, or resharing a blog post via Twitter.
It is also easy to implicitly create links between contextual identities,
sometimes accidentally: generating two isomorphic graphs at different services
is often enough to re-identify an individual~\cite{narayanan1}. The plethora of
cross-posting software available suggests that users often want to link
identities.

Building reputation online is a long and arduous process; a user who has built
up high credibility in one social network may want to transfer that credibility
when using a new service by using the same identifier or somehow proving in the
new service that they control other existing, credible identities.  The rise of
verified account mechanisms in Twitter, Google Plus and Facebook indicates that
this is a real problem.

@@

All five major browsers (Firefox, Chrome, Safari, Internet Explorer, and Opera)
offer synchronizing some set of browser data across devices, with varying
degrees of success. Multiple cross-browser applications also exist to
synchronize bookmarks and passwords~\footnote{Bookmark sync: \url{xmarks.com}, password sync: \url{lastpass.com}}.

@@

Given the large number of social network users and that 30-40\% of spoken
communication is devoted to informing others about ourselves, many users are
bound to share personal information online that they regret~\cite{tamir}.

@@

Service providers are highly incentivized to make linking identities easy;
more tools to help separate and curate identities are necessary. Without
knowing more about how users think about identity, we concentrate solely on
automating manual processes that users already perform.

@@

\paragraph{Mitigating accidental linkage} Federated login services can prevent
linking contextual identities to the same user identifier. For example, a
federated login service that supported multiple identifiers could prevent the
user from associating the same identifier to radically different
contextual identities, such as ones for dating and professional use.

@@

\paragraph{Expiring posts}
Humans don't have perfect memories, and neither should social
networks~\cite{delete}. Many users already engage in manual auditing and
deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
that let the user manage this more easily through an API: both Twitter and
Facebook provide APIs for post deletion\footnote{Google Plus offers a read-only
API.}.

@@

\section{Summary}
People have multiple contextual identities. Sharing personal information in
appropriate contexts fosters positive human interaction.  We hope that
contextual identity serves as a useful notion for developers to understand
their users' privacy needs and develop tools to help users manage their
identities.
